Sequence assembly

### 2024-04-03 episodes/phylogenetics.Rmd
Adapting a few more episodes to Uppmax

We will now use IQ-TREE to infer a maximum-likelihood (ML) tree of the RpoB dataset we aligned with `mafft` previously. While you performed the first trees on your laptop, you will infer the ML tree on Uppmax. As usual, use the `interactive` command to gain access to compute time. Go to the `phylogentics` folder created in the MSA episode, and load the right modules.

@@

```bash
$ iqtree2 -s rpoB.einsi.clipkit.aln -m TEST -B 1000
```

@@

```bash
$ iqtree2 -s rpoB.fftns.aln -m TEST -B 1000
$ figtree rpoB.fftns.aln.treefile &
```

>>>>

We will now use IQ-TREE to infer a maximum-likelihood (ML) tree of the RpoB dataset we aligned with `mafft` previously. While you performed the first trees on your laptop, you will infer the ML tree on Uppmax. As usual, use the `interactive` command to gain access to compute time. Go to the `phylogenetics` folder created in the MSA episode, and load the right modules.

@@

```bash
iqtree2 -s rpoB.einsi.clipkit.aln -m TEST -B 1000
```

@@

```bash
iqtree2 -s rpoB.fftns.aln -m TEST -B 1000
```

Import the tree on your computer and load it with FigTree or with [phylo.io](https://beta.phylo.io/viewer/#)

```bash
figtree rpoB.fftns.aln.treefile &
```

### 2024-04-03 episodes/sequence-assembly.Rmd
Fixing a few issues with Mobaxterm on Windows and not waiting for the blast to complete.
Adapting a few more episodes to Uppmax

```bash
$ mkdir ~/molepi/results/assembly
$ cd ~/molepi/data/trimmed_fastq
```

@@

```bash
$ for sample in ERR029206
do
skesa \
--cores 2 \
--memory 8 \
--fastq "${sample}"_1.fastq.gz_trim.fastq "${sample}"_2.fastq.gz_trim.fastq 1> ../../results/assembly/"${sample}".fasta
done
```

@@

## Challenge: What do the command line parameters of SKESA mean??

@@

```
$ skesa -h
```

@@

```output
$ skesa -h
..
General options:
-h [ --help ]                 Produce help message
-v [ --version ]              Print version
..
--cores arg (=0)              Number of cores to use (default all) [integer]
--memory arg (=32)            Memory available (GB, only for sorted counter)
..  
--fastq arg                   Input fastq file(s) (could be used multiple times for different runs) [string]
..
..
```

@@

## Exercise: How many contigs were generated by SKESA??

>>>>

```bash
mkdir ~/molepi/results/assembly
cd ~/molepi/data/trimmed_fastq
```

@@

```bash
for sample in ERR029206
do
skesa \
--cores 2 \
--memory 8 \
--fastq "${sample}"_1.fastq.gz_trim.fastq "${sample}"_2.fastq.gz_trim.fastq 1> ../../results/assembly/"${sample}".fasta
done
```

@@

## Challenge: What do the command line parameters of SKESA mean?

@@

```bash 
skesa -h
```

@@

```output
skesa -h
..
General options:
-h [ --help ]                 Produce help message
-v [ --version ]              Print version
..
--cores arg (=0)              Number of cores to use (default all) [integer]
--memory arg (=32)            Memory available (GB, only for sorted counter)
..  
--fastq arg                   Input fastq file(s) (could be used multiple times for different runs) [string]
..
..
```

@@

## Challenge: How many contigs were generated by SKESA?
